---
# title: "About"
---

# 6.4 Robustness Tests {#sec-result-robustness-tests}

In this chapter, we assess the robustness of the main results and address potential limitations of the analysis. To do so, we conduct several alterations to the model specification and its variables. These modifications aim to evaluate the stability and reliability of our final specification, as detailed in @eq-main_2. The results are presented in @tbl-regression-robust-testing with Model 1 representing the main specification of @eq-main_2, corresponding to Model 6 in @tbl-main-results.

## Outliers and Potential Data Errors

In Models 2 to 4, we alter the control and dependent variables by removing potential outliers and data errors to assess the robustness of our main results. In Model 2, we remove observations with sales prices greater than DKK 10 million (EUR 1.3 million). In Model 3, we exclude observations where the price per square metre is less than DKK \[XX\] (EUR 39) or greater than DKK 95,000 (EUR 12,350).

In Model 4, we remove observations based on selected control variables. Specifically, we exclude properties where the energy source is unknown, properties with more than four bathrooms or no bathroom, properties with more than four toilets, and properties with more than seven rooms or no rooms. In Model 5, we combine all the criteria from Models 2 to 4.

Across Models 2 to 5, the key variables do not appear to change substantially in terms of their signs or statistical significance. However, similar to the results found for the property-type segment, Model 5 shows that, on average, the most energy-efficient EPC label, A2020, does not appear to outperform label A2015 in terms of its price premium. This result provides further evidence of a potential non-linear relationship between energy efficiency and property prices. While energy-efficient properties are generally valued more highly than less energy-efficient properties, there appears to be a threshold beyond which additional improvements in energy efficiency do not translate into additional property value.

Regarding model fit, Model 5 produces a within $R^2$ of up to 0.527, compared with 0.442 in our main specification (Model 6 in @tbl-main-results). This indicates that Model 5 explains 52.7% of the variation in property prices within the fixed-effects clusters.

## Energy Consumption

Furthermore, we utilise the energy consumption of dwellings as an alternative measure of energy efficiency. In this specification, $EE_i$ in @eq-main_2 represents the natural logarithm of the estimated annual energy consumption of dwelling $i$, measured in kWh.

The purpose of using energy consumption is to assess whether the findings are consistent with those obtained using EPC labels. If a price premium is found for energy-efficient labels, where estimated energy consumption is an important determinant of these labels, one would expect energy consumption to produce similar results. Specifically, higher energy consumption should be associated with larger price discounts.

However, if this is not the case, one possible explanation is that the signalling effect of EPC labels is more important to consumers than the underlying estimated energy consumption. Consumers may not necessarily expect their actual energy consumption to correspond to the amount reported in the EPC report. This argument is consistent with the findings of @wahlstrom_doing_2016.

For this interpretation to hold, however, we must assume that the EPC labels are genuinely capturing a signalling effect rather than incorporating other potential effects, such as omitted variables or measurement errors. Alternatively, differences between the effects of EPC labels and energy consumption could indicate potential bias or measurement error in our regression.

The results are presented in Model 6 and support the findings from the main analysis. Energy consumption has a negative and statistically significant effect on property prices at the 1% level. Based on the estimated coefficient, a 1% increase in energy consumption is associated with a 9.7% decrease in property prices. This result indicates that property prices are relatively elastic with respect to estimated energy consumption.

It is worth noting that, due to limitations in the data extraction process from the EPC reports, we were unable to extract estimated energy consumption for all properties. This is due both to data errors and to the fact that many EPC reports do not provide an estimate of energy consumption. Consequently, the sample used when analysing energy consumption contains 582,690 observations, which is approximately 20% smaller than the full sample used in the main analysis.

## Time on the Market

Next, we address potential bias related to the relationship between price and demand by using time on the market as a proxy for demand. This approach addresses the possibility that lower transaction prices may be associated with longer selling periods due to lower demand.

By analysing how quickly energy-efficient properties sell in addition to their transaction prices, we can assess whether the observed effects of energy efficiency are also reflected in market liquidity and are therefore not solely driven by price mechanisms.

The results are presented in Model 7 and further complement the main findings, as well as the previous evidence regarding a potential non-linear relationship between energy efficiency and property prices. Using time on the market as an alternative outcome measure, we find that A2010 properties sell the fastest, followed by A2020 and A2015 properties. This pattern reinforces the observed non-linear relationship between energy efficiency and property prices.

Model 7 shows that properties labelled A2020, A2015, and A2010 are sold, on average, 31, 24, and 34 days faster than D-labelled properties, respectively. Properties labelled B and C are sold, on average, 18 and 16 days faster than D-labelled properties. Conversely, properties labelled E, F, and G, which are less energy-efficient, take, on average, 13, 22, and 26 days longer to sell than D-labelled properties.

Additionally, these results are consistent with insights provided by real estate agents, as discussed in @sec-epbd-danish-epc-scheme.

<!-- Regression table 10  -->

::: {#tbl-regression-robust-testing}
```{r}
#| echo: false
#| warning: false
#| message: false

# ************************************************************************************************
# ================================================================================================ 
#  CREATING THE DATAFRAME - with all the results 
# ================================================================================================ 
# ************************************************************************************************


# Load required libraries
library(gt)
library(dplyr)
 

# Function to create the robustness testing table
create_robustness_table <- function() {
  
  # Initialize empty dataframe
  df <- data.frame(
    section = character(),
    variable = character(),
    col1 = character(),
    col2 = character(),
    col3 = character(),
    col4 = character(),
    col5 = character(),
    col6 = character(),
    col7 = character(),
    stringsAsFactors = FALSE
  )
  
  # ============================================================
  # SECTION 0: Log(Total heating demand)
  # ============================================================
  
  heating_demand <- data.frame(
    # section = rep("Log(Total heating demand in kWh)", 2),
    section = rep("Heating Demand in kWh", 2),
    variable = c(
      "Log(Total heating demand in kWh)", ""
    ),
    col1 = c("", ""),
    col2 = c("", ""),
    col3 = c("", ""),
    col4 = c("", ""),
    col5 = c("", ""),
    col6 = c("-0.097***", "(0.002)"),
    col7 = c("", ""),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, heating_demand)
  
  # ============================================================
  # SECTION 1: Current Energy label (D as reference)
  # ============================================================
  
  energy_labels <- data.frame(
    section = rep("Current Energy label: D as a reference category", 16),
    variable = c(
      "EPC label A2020", "", 
      "EPC label 2015", "",
      "EPC label 2010", "",
      "EPC label B", "",
      "EPC label C", "",
      "EPC label E", "",
      "EPC label F", "",
      "EPC label G", ""
    ),
    col1 = c("0.074***", "(0.009)", "0.062***", "(0.007)", "0.026***", "(0.004)",
             "0.022***", "(0.003)", "0.020***", "(0.002)", "-0.060***", "(0.002)",
             "-0.118***", "(0.003)", "-0.252***", "(0.004)"),
    col2 = c("0.069***", "(0.008)", "0.070***", "(0.006)", "0.030***", "(0.004)",
             "0.022***", "(0.002)", "0.024***", "(0.001)", "-0.060***", "(0.002)",
             "-0.117***", "(0.003)", "-0.245***", "(0.004)"),
    col3 = c("0.066***", "(0.007)", "0.067***", "(0.006)", "0.037***", "(0.004)",
             "0.026***", "(0.002)", "0.027***", "(0.001)", "-0.057***", "(0.002)",
             "-0.118***", "(0.002)", "-0.239***", "(0.004)"),
    col4 = c("0.071***", "(0.009)", "0.061***", "(0.007)", "0.024***", "(0.004)",
             "0.020***", "(0.003)", "0.020***", "(0.002)", "-0.060***", "(0.002)",
             "-0.114***", "(0.003)", "-0.246***", "(0.004)"),
    col5 = c("0.062***", "(0.007)", "0.067***", "(0.006)", "0.036***", "(0.004)",
             "0.025***", "(0.002)", "0.028***", "(0.001)", "-0.057***", "(0.002)",
             "-0.116***", "(0.003)", "-0.236***", "(0.004)"),
    col6 = c("", "", "", "", "", "", "", "", "", "", "", "", "", "", "", ""),
    col7 = c("-30.693***", "(4.161)", "-23.828***", "(3.048)", "-33.997***", "(2.152)",
             "-18.149***", "(1.306)", "-14.604***", "(0.743)", "13.212***", "(0.909)",
             "22.218***", "(1.426)", "25.901***", "(2.189)"),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, energy_labels)
  
  # ============================================================
  # SECTION 2: Energy source
  # ============================================================
  
  energy_source <- data.frame(
    section = rep("Energy source: with District heating as reference category", 26),
    variable = c(
      "Natural Gas", "",
      "Oil", "",
      "Wood and District heating", "",
      "Wood pellets", "",
      "Wood and electricity", "",
      "Electricity and Wood pellets", "",
      "Electricity and District heating", "",
      "Electricity and Natural gas", "",
      "Electricity", "",
      "Wood", "",
      "Unknown", "",
      "Other source combination", "",
      "Electricity and Oil", ""
    ),
    col1 = c("-0.026***", "(0.003)", "-0.101***", "(0.004)", "-0.016", "(0.011)",
             "-0.006", "(0.007)", "0.007", "(0.004)", "-0.034***", "(0.006)",
             "0.053***", "(0.004)", "-0.021***", "(0.004)", "0.019***", "(0.003)",
             "-0.029**", "(0.012)", "0.008", "(0.005)", "-0.028***", "(0.008)",
             "-0.122***", "(0.006)"),
    col2 = c("-0.031***", "(0.002)", "-0.107***", "(0.004)", "-0.016", "(0.010)",
             "0.002", "(0.006)", "-0.005", "(0.004)", "-0.033***", "(0.006)",
             "0.043***", "(0.003)", "-0.028***", "(0.004)", "0.008***", "(0.003)",
             "-0.029**", "(0.012)", "0.010**", "(0.005)", "-0.031***", "(0.007)",
             "-0.126***", "(0.006)"),
    col3 = c("-0.034***", "(0.002)", "-0.112***", "(0.003)", "-0.005", "(0.010)",
             "-0.006", "(0.006)", "-0.009**", "(0.004)", "-0.038***", "(0.005)",
             "0.041***", "(0.003)", "-0.030***", "(0.004)", "0.003", "(0.003)",
             "-0.041***", "(0.011)", "0.006", "(0.004)", "-0.036***", "(0.007)",
             "-0.128***", "(0.006)"),
    col4 = c("-0.026***", "(0.003)", "-0.101***", "(0.004)", "-0.011", "(0.012)",
             "-0.004", "(0.007)", "0.010**", "(0.005)", "-0.035***", "(0.006)",
             "0.054***", "(0.004)", "-0.020***", "(0.004)", "0.017***", "(0.003)",
             "-0.026**", "(0.013)", "", "", "-0.028***", "(0.008)",
             "-0.123***", "(0.007)"),
    col5 = c("-0.034***", "(0.002)", "-0.111***", "(0.004)", "0.001", "(0.010)",
             "-0.001", "(0.006)", "-0.006", "(0.004)", "-0.037***", "(0.006)",
             "0.042***", "(0.003)", "-0.029***", "(0.004)", "0.003", "(0.003)",
             "-0.035***", "(0.012)", "", "", "-0.035***", "(0.008)",
             "-0.130***", "(0.006)"),
    col6 = c("-0.047***", "(0.003)", "-0.143***", "(0.005)", "-0.039**", "(0.019)",
             "-0.027***", "(0.008)", "-0.085***", "(0.005)", "-0.070***", "(0.007)",
             "0.050***", "(0.004)", "-0.057***", "(0.005)", "-0.097***", "(0.004)",
             "-0.094***", "(0.017)", "", "", "-0.087***", "(0.010)",
             "-0.182***", "(0.007)"),
    col7 = c("19.794***", "(1.372)", "39.084***", "(2.185)", "26.679***", "(7.633)",
             "4.254", "(3.852)", "26.970***", "(2.578)", "9.913***", "(3.234)",
             "8.677***", "(1.690)", "27.378***", "(2.242)", "21.111***", "(1.684)",
             "40.707***", "(8.511)", "3.693", "(3.204)", "26.002***", "(4.274)",
             "40.534***", "(3.490)"),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, energy_source)
  
  # ============================================================
  # SECTION 3: Green Energy systems
  # ============================================================
  
  green_energy <- data.frame(
    section = rep("Green Energy systems", 6),
    variable = c(
      "Heat pump", "",
      "Solar-cells", "",
      "Solar-heating", ""
    ),
    col1 = c("0.007***", "(0.002)", "0.033***", "(0.002)", "0.019***", "(0.002)"),
    col2 = c("0.008***", "(0.001)", "0.029***", "(0.002)", "0.014***", "(0.002)"),
    col3 = c("0.004***", "(0.001)", "0.023***", "(0.002)", "0.013***", "(0.002)"),
    col4 = c("0.008***", "(0.002)", "0.032***", "(0.002)", "0.018***", "(0.002)"),
    col5 = c("0.004***", "(0.001)", "0.023***", "(0.002)", "0.012***", "(0.002)"),
    col6 = c("0.017***", "(0.002)", "0.032***", "(0.002)", "0.020***", "(0.002)"),
    col7 = c("-5.651***", "(0.762)", "-3.365***", "(0.942)", "-2.632***", "(0.952)"),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, green_energy)
  
  # ============================================================
  # SECTION 4: Renovation costs and benefits
  # ============================================================
  
  renovation_costs <- data.frame(
    section = rep("Renovation costs and benefits", 4),
    variable = c(
      "log(TICP + 1)", "",
      "log(TECS + 1)", ""
    ),
    col1 = c("-0.001***", "(0.000)", "-0.007***", "(0.000)"),
    col2 = c("-0.001***", "(0.000)", "-0.008***", "(0.000)"),
    col3 = c("-0.001***", "(0.000)", "-0.007***", "(0.000)"),
    col4 = c("-0.001***", "(0.000)", "-0.007***", "(0.000)"),
    col5 = c("-0.001***", "(0.000)", "-0.007***", "(0.000)"),
    col6 = c("-0.002***", "(0.000)", "-0.005***", "(0.000)"),
    col7 = c("0.650***", "(0.084)", "-0.383**", "(0.185)"),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, renovation_costs)
  
  # ============================================================
  # SECTION 5: Label Jump
  # ============================================================
  
  label_jump <- data.frame(
    section = rep("Label Jump (Distance from current label to the potential label): with zero (no label jump) as reference category", 16),
    variable = c(
      "Jump up by 1 label", "",
      "Jump up by 2 labels", "",
      "Jump up by 3 labels", "",
      "Jump up by 4 labels", "",
      "Jump up by 5 labels", "",
      "Jump up by 6 labels", "",
      "Jump up by 7 labels", "",
      "Jump up by 8 labels", ""
    ),
    col1 = c("0.004**", "(0.002)", "0.023***", "(0.002)", "0.036***", "(0.003)",
             "0.026***", "(0.003)", "0.019***", "(0.005)", "-0.014*", "(0.007)",
             "-0.012", "(0.013)", "-0.062***", "(0.019)"),
    col2 = c("0.011***", "(0.001)", "0.029***", "(0.002)", "0.034***", "(0.002)",
             "0.026***", "(0.003)", "0.025***", "(0.005)", "-0.007", "(0.007)",
             "-0.004", "(0.013)", "-0.072***", "(0.019)"),
    col3 = c("0.016***", "(0.001)", "0.026***", "(0.002)", "0.029***", "(0.002)",
             "0.020***", "(0.003)", "0.013***", "(0.004)", "-0.014**", "(0.007)",
             "-0.011", "(0.013)", "-0.073***", "(0.019)"),
    col4 = c("0.004***", "(0.002)", "0.023***", "(0.002)", "0.037***", "(0.003)",
             "0.026***", "(0.004)", "0.020***", "(0.005)", "-0.015*", "(0.008)",
             "-0.011", "(0.014)", "-0.063***", "(0.020)"),
    col5 = c("0.017***", "(0.001)", "0.026***", "(0.002)", "0.030***", "(0.002)",
             "0.020***", "(0.003)", "0.014***", "(0.004)", "-0.014**", "(0.007)",
             "-0.013", "(0.013)", "-0.074***", "(0.019)"),
    col6 = c("0.002", "(0.002)", "0.010***", "(0.002)", "0.003", "(0.003)",
             "-0.024***", "(0.004)", "-0.033***", "(0.005)", "-0.084***", "(0.008)",
             "-0.086***", "(0.015)", "-0.227***", "(0.021)"),
    col7 = c("-24.556***", "(0.826)", "-28.811***", "(1.005)", "-35.910***", "(1.329)",
             "-37.616***", "(1.785)", "-44.479***", "(2.419)", "-48.798***", "(3.842)",
             "-56.404***", "(6.782)", "-49.523***", "(11.120)"),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, label_jump)
  
  # ============================================================
  # SECTION 6: Type of renovations needed (from second table)
  # ============================================================
  
  renovations <- data.frame(
    section = rep("Type of renovations needed", 24),
    variable = c(
      "Roof and attic renovation", "",
      "Walls renovation", "",
      "Install Solar-cells", "",
      "Heating system renovation", "",
      "Water system renovation", "",
      "Floor renovation", "",
      "Window and door renovation", "",
      "Install heatpumps", "",
      "Other renovations", "",
      "Install solar-heating", "",
      "Ventilation renovation", "",
      "Install District heating", ""
    ),
    col1 = c("-0.020***", "(0.001)", "-0.006***", "(0.001)", "0.004***", "(0.001)",
             "-0.016***", "(0.001)", "0.005***", "(0.001)", "-0.044***", "(0.001)",
             "-0.054***", "(0.001)", "-0.009***", "(0.002)", "-0.025***", "(0.001)",
             "0.001", "(0.002)", "-0.006", "(0.004)", "0.069***", "(0.009)"),
    col2 = c("-0.021***", "(0.001)", "-0.005***", "(0.001)", "0.003***", "(0.001)",
             "-0.009***", "(0.001)", "-0.002", "(0.001)", "-0.039***", "(0.001)",
             "-0.053***", "(0.001)", "-0.007***", "(0.002)", "-0.020***", "(0.001)",
             "0.001", "(0.002)", "-0.007**", "(0.003)", "0.073***", "(0.009)"),
    col3 = c("-0.024***", "(0.001)", "-0.006***", "(0.001)", "0.001", "(0.001)",
             "-0.008***", "(0.001)", "-0.002*", "(0.001)", "-0.033***", "(0.001)",
             "-0.056***", "(0.001)", "-0.003*", "(0.002)", "-0.016***", "(0.001)",
             "0.000", "(0.001)", "-0.008***", "(0.003)", "0.051***", "(0.008)"),
    col4 = c("-0.020***", "(0.001)", "-0.006***", "(0.001)", "0.005***", "(0.001)",
             "-0.015***", "(0.001)", "0.004**", "(0.002)", "-0.043***", "(0.001)",
             "-0.052***", "(0.001)", "-0.009***", "(0.002)", "-0.024***", "(0.001)",
             "0.001", "(0.002)", "-0.005", "(0.004)", "0.066***", "(0.009)"),
    col5 = c("-0.023***", "(0.001)", "-0.006***", "(0.001)", "0.002", "(0.001)",
             "-0.007***", "(0.001)", "-0.003**", "(0.001)", "-0.031***", "(0.001)",
             "-0.053***", "(0.001)", "-0.004*", "(0.002)", "-0.015***", "(0.001)",
             "0.001", "(0.001)", "-0.007**", "(0.003)", "0.046***", "(0.008)"),
    col6 = c("-0.024***", "(0.001)", "-0.007***", "(0.001)", "0.012***", "(0.002)",
             "-0.021***", "(0.001)", "0.000", "(0.002)", "-0.052***", "(0.002)",
             "-0.057***", "(0.002)", "0.005**", "(0.002)", "-0.021***", "(0.001)",
             "-0.002", "(0.002)", "-0.009**", "(0.004)", "0.060***", "(0.010)"),
    col7 = c("6.494***", "(0.622)", "3.954***", "(0.688)", "-7.355***", "(0.692)",
             "2.070***", "(0.646)", "0.927", "(0.746)", "-2.682***", "(0.678)",
             "0.601", "(0.723)", "-3.493***", "(1.096)", "-4.027***", "(0.631)",
             "4.014***", "(0.857)", "3.422**", "(1.634)", "-3.015", "(3.747)"),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, renovations)
  
  # ============================================================
  # SECTION 7: Controls and Summary Statistics - REORDERED
  # ============================================================
  
  controls <- data.frame(
    section = rep("", 11),  # Empty section - no header will appear
    variable = c(
      # Model fit statistics first (on top)
      "R²",
      "R² Adjusted",
      "R² Within Adjusted",
      "RMSE",
      "Number of Observations",
      # Then controls
      "Property characteristics controls",
      "Property quality controls",
      "Geographical controls",
      "Time Fixed effects (Month and Year)",
      "Place Fixed effects (4-digit postal code)",
      "Time × Place Fixed effect"
    ),
    col1 = c("0.7571", "0.7156", "0.4420", "0.3803", "728,794", 
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col2 = c("0.7702", "0.7303", "0.4726", "0.3454", "716,057",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col3 = c("0.8025", "0.7678", "0.5358", "0.3195", "710,593",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col4 = c("0.7580", "0.7154", "0.4367", "0.3763", "694,670",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col5 = c("0.8013", "0.7652", "0.5277", "0.3136", "675,477",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col6 = c("0.7657", "0.7186", "0.4345", "0.3687", "582,690",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col7 = c("0.3511", "0.2146", "0.0356", "162.4148", "570,282",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, controls)
  
  return(df)
}

# Create the table data
table_data <- create_robustness_table()

```

```{r}
#| echo: false
#| warning: false
#| message: false



# ************************************************************************************************
# ================================================================================================ 
#  ADD HTML style to fixed effects 
# ================================================================================================ 
# ************************************************************************************************


# Function to create badge HTML
create_badge <- function(value) {
  if (value == "Yes") {
    return('<span style="display: inline-block; padding: 2px 12px; background-color: #4CAF50; color: white; border-radius: 12px; font-size: 11px; font-weight: 500; opacity: 0.85; text-align: center;">✓ Yes</span>')
  } else if (value == "No") {
    return('<span style="display: inline-block; padding: 2px 12px; background-color: #f44336; color: white; border-radius: 12px; font-size: 11px; font-weight: 500; opacity: 0.85; text-align: center;">✗ No</span>')
  } else {
    return(value)
  }
}

# Apply badge formatting to Yes/No values in the dataframe
table_data_formatted <- table_data %>%
  mutate(
    col1 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col1, create_badge), col1),
    col2 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col2, create_badge), col2),
    col3 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col3, create_badge), col3),
    col4 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col4, create_badge), col4),
    col5 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col5, create_badge), col5),
    col6 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col6, create_badge), col6),
    col7 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col7, create_badge), col7)
  )


```

```{r}
#| echo: false
#| warning: false
#| message: false


# ************************************************************************************************
# ================================================================================================ 
#  Style the TABLE AND SHOW
# ================================================================================================ 
# ************************************************************************************************


# Create the gt table with colored badges
table_data_formatted %>%
  gt(
    groupname_col = "section"
  ) %>%
  tab_header(
    title = md("**Robustness Testing**")
  ) %>%
  tab_spanner(
    label = md("**Dependent variables**"),
    columns = c(col1, col2, col3, col4, col5, col6, col7)
  ) %>%
  cols_label(
    variable = "",
    col1 = "(1) Ln(Price)",
    col2 = "(2) Ln(Price)",
    col3 = "(3) Ln(Price)",
    col4 = "(4) Ln(Price)",
    col5 = "(5) Ln(Price)",
    col6 = "(6) Ln(Price)",
    col7 = "(7) Advertisement Duration"
  ) %>%
  # Style the section headers (row groups)
  tab_style(
    style = list(
      cell_text(weight = "bold", style = "italic", size = px(14)),
      cell_borders(sides = "bottom", color = "black", weight = px(1.5))
    ),
    locations = cells_row_groups()
  ) %>%
  # Allow HTML in the table cells
  fmt_markdown(
    columns = c(col1, col2, col3, col4, col5, col6, col7)
  ) %>%
  # Bold the significance stars in the table
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = c(col1, col2, col3, col4, col5, col6, col7),
      rows = grepl("\\*\\*\\*|\\*\\*|\\*", 
                   paste(table_data_formatted$col1, table_data_formatted$col2, 
                         table_data_formatted$col3, table_data_formatted$col4, 
                         table_data_formatted$col5, table_data_formatted$col6,
                         table_data_formatted$col7))
    )
  ) %>%
  # Make R² values bold
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      rows = table_data_formatted$variable %in% c("R²", "R² Adjusted", "R² Within Adjusted")
    )
  ) %>%
  tab_options(
    table.font.size = px(11),
    heading.title.font.size = px(16),
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold",
    row_group.font.size = px(12),
    table.width = pct(100),
    row_group.padding = px(10)
  ) %>%
  # Use tab_source_note for footnote
  tab_source_note(
    source_note = md("Heteroscedasticity-robust standard errors in parentheses. Indicators of significance level: * p < 0.1, ** p < 0.05, *** p < 0.01. Dependent variable: Natural logarithm of transaction price. TICP - Total investments cost for profitable renovations. TECS - Total energy cost saved from all renovations. Models 1 to 5 are in line with Equation ref{eq:finalRegression}. In Model 6 we switch EPC labels for the natural logarithm of total heating demand in kWh and in Model 7 we set the dependent variable to the number of days the property was advertised.")
  )
```
:::

## Robustness of Text Classification

Finally, we assess the robustness of the observed price premiums associated with solar heating, solar cells, and heat pumps, as reported in the main results (Model 6 in @tbl-main-results). We do this by estimating multiple models based on @eq-main_2 while continuously increasing the probability threshold used to classify the three variables.

The findings are presented in @tbl-robust-test-text-classification. As before, Model 1 represents the main specification, using an 85% probability threshold for all three variables. For Models 2 through 7, the probability thresholds are increased to 90%, 95%, 96%, 97%, 98%, and 99%, respectively.

For solar heating and solar cells, the coefficients are relatively stable, with only minor changes, and remain statistically significant at the 1% level across all specifications.

Interestingly, as the probability threshold for solar cells increases, the estimated price premium also increases, ranging from 3.35% to 4.48%. In contrast, the price premium associated with solar heating decreases as the probability threshold increases, ranging from 1.0% to 1.9%.

For heat pumps, the statistical significance changes from the 1% level in Model 1 to the 5% level for probability thresholds between 95% and 97%, before returning to the 1% level at the 98% and 99% thresholds. However, the estimated coefficient for heat pumps changes only marginally, ranging from 0.40% to 0.72%.

Moreover, the coefficients of the other key variables and control variables do not appear to change substantially as the probability threshold increases. It is worth noting that although increasing the probability threshold improves the precision of the classification by reducing the number of false-positive observations, this comes at the potential cost of increasing the number of false-negative observations.

Nevertheless, regardless of the probability threshold applied, all three components have a positive estimated effect on property prices. However, the relatively small and less stable coefficient for heat pumps suggests that home buyers may place less value on heat pumps compared with solar cells and solar heating.

<!-- Regression table 11  -->

::: {#tbl-robust-test-text-classification}
```{r}
#| echo: false
#| warning: false
#| message: false

# Function to create the text classification robustness table
create_text_classification_table <- function() {
  
  # Initialize empty dataframe
  df <- data.frame(
    section = character(),
    variable = character(),
    col1 = character(),
    col2 = character(),
    col3 = character(),
    col4 = character(),
    col5 = character(),
    col6 = character(),
    col7 = character(),
    stringsAsFactors = FALSE
  )
  
  # ============================================================
  # SECTION 1: Green Energy systems
  # ============================================================
  
  green_energy <- data.frame(
    section = rep("Green Energy systems", 6),
    variable = c(
      "Heat pump", "",
      "Solar-cells", "",
      "Solar-heating", ""
    ),
    col1 = c("0.007***", "(0.002)", "0.033***", "(0.002)", "0.019***", "(0.002)"),
    col2 = c("0.004**", "(0.002)", "0.041***", "(0.002)", "0.018***", "(0.002)"),
    col3 = c("0.004**", "(0.002)", "0.042***", "(0.003)", "0.013***", "(0.002)"),
    col4 = c("0.004**", "(0.002)", "0.042***", "(0.003)", "0.014***", "(0.002)"),
    col5 = c("0.004**", "(0.002)", "0.043***", "(0.003)", "0.014***", "(0.003)"),
    col6 = c("0.005***", "(0.002)", "0.047***", "(0.003)", "0.011***", "(0.003)"),
    col7 = c("0.007***", "(0.002)", "0.047***", "(0.003)", "0.010***", "(0.003)"),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, green_energy)
  
  # ============================================================
  # SECTION 2: Controls and Summary Statistics - REORDERED
  # ============================================================
  
  controls <- data.frame(
    section = rep("", 11),  # Empty section - no header will appear
    variable = c(
      # Model fit statistics first (on top)
      "R²",
      "R² Adjusted",
      "R² Within Adjusted",
      "RMSE",
      "Number of Observations",
      # Then controls
      "Property characteristics controls",
      "Property quality controls",
      "Geographical controls",
      "Time Fixed effects (Month and Year)",
      "Place Fixed effects (4-digit postal code)",
      "Time × Place Fixed effect"
    ),
    col1 = c("0.7571", "0.7156", "0.4420", "0.3803", "728,794", 
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col2 = c("0.7571", "0.7156", "0.4420", "0.3803", "728,794",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col3 = c("0.7570", "0.7156", "0.4419", "0.3803", "728,795",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col4 = c("0.7570", "0.7155", "0.4419", "0.3803", "728,795",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col5 = c("0.7570", "0.7155", "0.4419", "0.3803", "728,794",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col6 = c("0.7570", "0.7155", "0.4419", "0.3803", "728,794",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    col7 = c("0.7570", "0.7155", "0.4419", "0.3804", "728,794",
             "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
    stringsAsFactors = FALSE
  )
  
  df <- rbind(df, controls)
  
  return(df)
}

# Create the table data
table_data <- create_text_classification_table()
```

```{r}
#| echo: false
#| warning: false
#| message: false

# Function to create badge HTML
create_badge <- function(value) {
  if (value == "Yes") {
    return('<span style="display: inline-block; padding: 2px 12px; background-color: #4CAF50; color: white; border-radius: 12px; font-size: 11px; font-weight: 500; opacity: 0.85; text-align: center;">✓ Yes</span>')
  } else if (value == "No") {
    return('<span style="display: inline-block; padding: 2px 12px; background-color: #f44336; color: white; border-radius: 12px; font-size: 11px; font-weight: 500; opacity: 0.85; text-align: center;">✗ No</span>')
  } else {
    return(value)
  }
}

# Apply badge formatting to Yes/No values in the dataframe
table_data_formatted <- table_data %>%
  mutate(
    col1 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col1, create_badge), col1),
    col2 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col2, create_badge), col2),
    col3 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col3, create_badge), col3),
    col4 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col4, create_badge), col4),
    col5 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col5, create_badge), col5),
    col6 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col6, create_badge), col6),
    col7 = ifelse(variable %in% c("Property characteristics controls", 
                                  "Property quality controls",
                                  "Geographical controls",
                                  "Time Fixed effects (Month and Year)",
                                  "Place Fixed effects (4-digit postal code)",
                                  "Time × Place Fixed effect"),
                  sapply(col7, create_badge), col7)
  )
```

```{r}
#| echo: false
#| warning: false
#| message: false

# Create the gt table with colored badges
table_data_formatted %>%
  gt(
    groupname_col = "section"
  ) %>%
  tab_header(
    title = md("**Robustness Test - Text Classification**")
  ) %>%
  tab_spanner(
    label = md("**Dependent variables: Ln(Price)**"),
    columns = c(col1, col2, col3, col4, col5, col6, col7)
  ) %>%
  tab_spanner(
    label = md("**Threshold**"),
    columns = c(col1, col2, col3, col4, col5, col6, col7)
  ) %>%
  cols_label(
    variable = "",
    col1 = "(1)<br>85%",
    col2 = "(2)<br>90%",
    col3 = "(3)<br>95%",
    col4 = "(4)<br>96%",
    col5 = "(5)<br>97%",
    col6 = "(6)<br>98%",
    col7 = "(7)<br>99%"
  ) %>%
  # Style the section headers (row groups)
  tab_style(
    style = list(
      cell_text(weight = "bold", style = "italic", size = px(14)),
      cell_borders(sides = "bottom", color = "black", weight = px(1.5))
    ),
    locations = cells_row_groups()
  ) %>%
  # Allow HTML in the table cells
  fmt_markdown(
    columns = c(col1, col2, col3, col4, col5, col6, col7)
  ) %>%
  # Bold the significance stars in the table
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = c(col1, col2, col3, col4, col5, col6, col7),
      rows = grepl("\\*\\*\\*|\\*\\*|\\*", 
                   paste(table_data_formatted$col1, table_data_formatted$col2, 
                         table_data_formatted$col3, table_data_formatted$col4, 
                         table_data_formatted$col5, table_data_formatted$col6,
                         table_data_formatted$col7))
    )
  ) %>%
  # Make R² values bold
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      rows = table_data_formatted$variable %in% c("R²", "R² Adjusted", "R² Within Adjusted")
    )
  ) %>%
  tab_options(
    table.font.size = px(12),
    heading.title.font.size = px(16),
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold",
    row_group.font.size = px(12),
    table.width = pct(100),
    row_group.padding = px(10)
  ) %>%
  # Use tab_source_note for footnote
  tab_source_note(
    source_note = md("Heteroscedasticity-robust standard errors in parentheses. Indicators of significance level: * p < 0.1, ** p < 0.05, *** p < 0.01. Dependent variable: Natural logarithm of transaction price. TICP - Total investments cost for profitable renovations. TECS - Total energy cost saved from all renovations.")
  )
```
:::